ECE498:~Senior Capstone Project I\\\textbf{\underline{Project Proposal}}\\ \vspace{0.5in} Project Title: Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle \vspace{1.0in} \author{Hannah Grady and Nicholas Nauman\\ Advisor: Dr.~Suruz Miah}

### 2022-02-02 proposal.tex
Update proposal.tex
I updated the paragraphs for the spring 2022 deliverables and added some headings. I also updated the Gantt chart for the spring semester.

 \begin{figure}
   \centering
   \begin{ganttchart}[
     hgrid,
     vgrid,
     x unit=.6cm,
     y unit title=.8cm,
     y unit chart=.6cm,
     milestone label font=\tiny,
     milestone progress label font = \tiny,
     milestone progress label anchor = east,
     bar label font=\tiny,
     group label font=\small,
     bar/.append style={fill=green},
     bar incomplete/.append style={fill=red},
     group progress label font = \tiny,
     progress label text={$\displaystyle#1\%$},
     group progress label anchor = east,
     bar progress label font = \tiny,
     bar progress label anchor = east,
     ]{1}{18}
     %\gantttitle{2021}{18}\\
     \gantttitle{Jan}{2}
     \gantttitle{Feb}{4}
     \gantttitle{Mar}{4}
     \gantttitle{Apr}{4}
     \gantttitle{May}{4}\\

%     \ganttgroup[progress = 0]{Assembly}{3}{4}\\
     \ganttbar[progress = 0]{Collect Shift, Speed Control, and Speed Data}{3}{3}\\
     \ganttbar[progress = 0]{Model Shift System}{3}{4}\\
     \ganttbar[progress = 0]{Model Speed Control System}{5}{6}\\
     \ganttbar[progress = 0]{Model Speed System}{7}{8}\\

%     \ganttgroup[progress = 10]{Software}{5}{6}\\
     \ganttbar[progress = 0]{Test Subsystems}{9}{12}\\
     \ganttmilestone[progress = 0]{Test Subsystems with HIL}{12}{15}\\

%     \ganttgroup[progress = 0]{Project Completion}{16}{17}\\
     \ganttmilestone[progress = 0]{Final Report}{15}{15}\\
     \ganttmilestone[progress = 0]{Final Presentation}{16}{16}\\
     \ganttbar[progress = 0]{Presentation to IAB}{17}{17}\\
     \ganttbar[progress = 0]{Project Demo}{17}{17}\\

@@

At the beginning of the spring semester we will present the work we have completed so far to Dr. Miah and to representatives from AutonomouStuff. This is to let them see how the project is progressing and what our plans are for this semester.

Once we have satisfactorily modeled the Steering, Acceleration, and Brake systems, we will then travel to AutonomouStuff and collect the necessary data for the Shift, Speed Control, and Speed subsystems. We will make sure to collect a large amount of data in order to ensure that we will get accurate models. This process should only take a day.

Once we have modeled our subsystems, we will then take these models and test them using AutonomouStuff’s Hardware in the Loop testbench. This allows us to see how our models will perform in the real world. Once these models have been tested, they will either be changed or kept as is.

We will create a presentation that outlines the work that we have completed up to this point as well as what we intend to complete for the remaining time of the project. We will be evaluated on our ability to demonstrate that we are making progress on the project and will be able to complete the goals that we set.

Around the time we test the subsystems using HIL, we will also demonstrate what we have worked on to representatives from AutonomouStuff. This is an important demonstration since AutonomouStuff has sponsored this senior project and is waiting to see if we have solved the problem of creating accurate mathematical models for their vehicle subsystems.

Similarly to the fall semester, we will give a complete presentation of the work we have done on this project and the resulting models we have come up with. This presentation will be conducted in front of a faculty panel, along with AutonomouStuff representatives and other interested parties. It will be the culmination of everything we have done over the course of the year.

The final report will sum up all of our efforts and findings for this project. It will contain all of the information so that readers will be able to understand how we generated the models and how we collected the necessary data. We will make sure to detail the steps we took and especially how we dealt with the non-linearity considerations for the steering system.

Near the end of the semester we will be presenting our work on this project to the Industrial Advisory Board, or IAB. This will allow the board to see some of the projects that the senior class has been working on this year. Since the IAB plays a large role in choosing senior projects, it will be important to show them the progress we have made on one of the projects they selected.

\begin{description}
\item[Collect shift, speed control, and speed data] $\ldots$

\item[Model shift system] $\ldots$

\item[Model speed control system] $\ldots$
\end{description}

>>>>

 \begin{figure}
   \centering
   \begin{ganttchart}[
     hgrid,
     vgrid,
     x unit=.6cm,
     y unit title=.8cm,
     y unit chart=.6cm,
     milestone label font=\tiny,
     milestone progress label font = \tiny,
     milestone progress label anchor = east,
     bar label font=\tiny,
     group label font=\small,
     bar/.append style={fill=green},
     bar incomplete/.append style={fill=red},
     group progress label font = \tiny,
     progress label text={$\displaystyle#1\%$},
     group progress label anchor = east,
     bar progress label font = \tiny,
     bar progress label anchor = east,
     ]{1}{18}
     %\gantttitle{2021}{18}\\
     \gantttitle{Jan}{2}
     \gantttitle{Feb}{5}
     \gantttitle{Mar}{4}
     \gantttitle{Apr}{4}
     \gantttitle{May}{4}\\

%     \ganttgroup[progress = 0]{Assembly}{3}{4}\\
     \ganttbar[progress = 0]{Collect Shift, Speed Control, and Speed Data}{4}{4}\\
     \ganttbar[progress = 0]{Model Shift, Speed Control, and Speed Subsystems}{4}{5}\\
     \ganttbar[progress = 0]{Progress Presentation}{6}{6}\\
%     \ganttbar[progress = 0]{Model Speed Control System}{5}{6}\\
%     \ganttbar[progress = 0]{Model Speed System}{7}{8}\\

%     \ganttgroup[progress = 10]{Software}{5}{6}\\
     \ganttbar[progress = 0]{Test Subsystems}{6}{7}\\
     \ganttmilestone[progress = 0]{Test Subsystems with HIL}{7}{7}\\
     \ganttbar[progress = 0]{AutonomouStuff Demo}{8}{9}\\

%     \ganttgroup[progress = 0]{Project Completion}{16}{17}\\
     \ganttmilestone[progress = 0]{Final Report}{15}{15}\\
     \ganttmilestone[progress = 0]{Final Presentation}{16}{16}\\
     \ganttbar[progress = 0]{Presentation to IAB}{17}{17}\\

@@

\begin{description}
\item[Progress presentation] 
We will create a presentation that outlines the work that we have completed up to this point as well as what we intend to complete for the remaining time of the project. We will be evaluated on our ability to demonstrate that we are making progress on the project and will be able to complete the goals that we set.

\item[Collect shift, speed control, and speed data] 
Once we have satisfactorily modeled the Steering, Acceleration, and Brake systems, we will then travel to AutonomouStuff and collect the necessary data for the shift, speed control, and speed subsystems. We will make sure to collect a large amount of data in order to ensure that we will get accurate models. This process should only take a day.

\item[Model shift, speed control, and speed subsystems] 
Once we have collected the necessary data from the Lexus vehicle, we will work on developing individual mathematical models for each subsystem. We will be using MATLAB’s System Identification Toolbox in order to try out different models and see which best represents each subsystem. These models will first be tested by us, and if they pass they will then be tested using AutonomouStuff’s HIL testbench.

\item[Test subsystems] 
Before we do any HIL testing, we will first work on testing the models ourselves in order to ensure that they are accurate. We are still determining the best way to test these models, but this is an important step since we do not want to take inaccurate models to be tested using the HIL testbench. Using an inaccurate model would cause us to lose time that could have been spent coming up with a better one.

\item[Test subsystems with HIL] 
Once we have modeled our subsystems, we will then take these models and test them using AutonomouStuff’s Hardware in the Loop testbench. This allows us to see how our models will perform in the real world. Once these models have been tested, they will either be changed or kept as is.

\item[AutonomouStuff demonstration] 
Around the time we test the subsystems using HIL, we will also demonstrate what we have worked on to representatives from AutonomouStuff. This is an important demonstration since AutonomouStuff has sponsored this senior project and is waiting to see if we have solved the problem of creating accurate mathematical models for their vehicle subsystems.

\item[Final report] 
The final report will sum up all of our efforts and findings for this project. It will contain all of the information so that readers will be able to understand how we generated the models and how we collected the necessary data. We will make sure to detail the steps we took and especially how we dealt with the non-linearity considerations for the steering system.

\item[Final presentation] 
Similarly to the fall semester, we will give a complete presentation of the work we have done on this project and the resulting models we have come up with. This presentation will be conducted in front of a faculty panel, along with AutonomouStuff representatives and other interested parties. It will be the culmination of everything we have done over the course of the year.

\item[Presentation to IAB] 
Near the end of the semester we will be presenting our work on this project to the Industrial Advisory Board, or IAB. This will allow the board to see some of the projects that the senior class has been working on this year. Since the IAB plays a large role in choosing senior projects, it will be important to show them the progress we have made on one of the projects they selected.

\end{description}
